TGI Spinal Analysis Code

### 2022-12-06 analysis/tgi-spinal_analysis.Rmd
beginning to regress...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
library(tidyverse)
library(gghalves)
library(ggpol)
```

@@

# ZOIB regression
Running main analysis of a zero inflated beta regression
Outcome: VAS
Predictors: manipulation (CNT, TGI), cold probe location ()
Run a seperate regression for each quality
# Cold
# Warm
# Burn

# Run one regression including quality as a predictor

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
library(tidyverse)
library(gghalves)
library(ggpol)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
```

@@

# ZOIB regression
Running main analysis of a zero inflated beta regression
Outcome: VAS
Predictors: manipulation (CNT, TGI), cold probe location ()
Run a seperate regression for each quality

```{r model_prep}
set.seed(1234)  # Make everything reproducible

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)

# recode cold_location and condition to reduce levels in regression
df_long$cold_cond[df_long$cold_probe == 'distal'] <- 'dist_rostr' 
df_long$cold_cond[df_long$cold_probe == 'rostral'] <- 'dist_rostr' 
df_long$cold_cond[df_long$cold_probe == 'proximal'] <- 'prox_caud' 
df_long$cold_cond[df_long$cold_probe == 'caudal'] <- 'prox_caud'

# to run zero inflated regressions need to make sure no values = 100, 
# as cannot model them, so simply minus a very small fraction from those values
df_long$beta <- ifelse(df_long$VAS==100, df_long$beta-0.0001, df_long$beta <- df_long$VAS)

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_long$beta <- df_long$beta/100
df_long$ID <- factor(df_long$ID)
```
# Cold
# Warm
# Burn

# Run one regression including quality as a predictor
```{r}
# Try and model all with ratings
model.all = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + quality + trial_n +
                                quality*manipulation*condition + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long,
                      na.action = na.omit) 
summary(model.all)
```
